|

### 2025-02-21 paper.Rmd
Add files via upload
Add one detail for the sum-to-zero constraint of the BYM2.
Add files via upload
Reverting back to initial formulation for BYM2
For how BYM2 is grouped: https://groups.google.com/g/r-inla-discussion-group/c/MvggAeodU78

The classical sum-to-zero identifiability constraint was used.
\item The BYM2 model, like other spatially-structure GMRF, relies on a neighbourhood matrix encoding the conditional dependencies between the data.

@@

\begin{equation*}
\begin{cases}
\mathrm{Parameters}
\begin{cases}
...next\\
\textbf{Models 3 to 6, spatial GMRF: GMRF with BYM2 structure for space}\\
\textbf{and exchangeable correlation structure between genotypes}\\
\mathrm{for}~f\in\{\alpha,\alpha'\},~(g_s,g_s')\in\{1,2\}^2,~\forall(z_s,z_s')\in \text{Set of postcodes}^2:\\
\mathrm{Latent~field}
\begin{cases}
f_{SPACE}(z_s,g_s) \sim 
BYM2\left(\sigma,\phi,R\right) \\
\Leftrightarrow \begin{cases}
f_{SPACE}(z_s,g_s) = \frac{1}{\sqrt{\tau_{f_{\text{SPACE}}}}}\left(\sqrt{1-\phi_{f_{\text{SPACE}}}}v(z_s,g_s)+\phi_{f_{\text{SPACE}}} u(z_s,g_s)\right)\\
v(z_s,g_s) \sim \mathcal{N}\left(0,1\right) \\
u(g_s) \sim \mathcal{N}\left(0,R_*^{-}\right) \\
\end{cases}\\
\mathrm{Corr}(u(z_s, 1),u(z_s, 2)) =\eta_{f_{\text{SPACE}}}
\end{cases}\\
\mathrm{Hyperparameters}
\begin{cases}
\eta_{f_{\text{SPACE}}}=  \frac{\exp(\eta_{f_{\text{SPACE}}}^*) - 1}{\exp(\eta_{f_{\text{SPACE}}}^*) + 2 - 1}\\
\eta_{f_{\text{SPACE}}}^* \sim \mathcal{N}\left(0,5\right)\\
\phi_{f_{SPACE}} \sim \mathcal{PC}_{\phi}\left(\lambda_{f_{SPACE}}\right)\\
\lambda_{f_{SPACE}} = \arg_{\in \mathbb{R}^+}: \Pr_{\lambda_{\sigma_{f_{\phi_{\text{SPACE}}}}}}\left(\phi_{f_{\text{SPACE}}}\leq\phi_{0}\right)=p_{\phi_{f_{\text{SPACE}}}}\\
\sigma_{f_{SPACE}} \sim \mathcal{PC}_{\sigma}\left(\lambda_{\sigma_{f_{SPACE}}}\right)\\
\lambda_{\sigma_{f_{SPACE}}} = -\frac{-\log\left(p_{\sigma_{f_{SPACE}}}\right)}{\sigma_{0}},~\Pr\left(\sigma >\sigma_{0}\right)=p_{\sigma_{f_{SPACE}}}\\
\left(\sigma_{0},p_{\sigma_{f_{SPACE}}}\right)=\left(10,0.01\right) \\
\left(\phi_{0},p_{\phi_{f_{SPACE}}}\right)=\left(0.5,0.5\right) \\
R :\begin{cases} 
\text{Delaunay Triangulation (model 3)}\\
\text{SOI subgraph of the Delaunay Triangulation (model 4)} \\
\text{1st-order Queen contiguity (model 5)} \\ 
\text{2nd-order Queen contiguity (model 6)} \\ 
\end{cases}\\
R_*:~\text{scaled counterpart of the matrix R}
\end{cases}
\end{cases}
\end{cases}
\end{equation*}
\newpage

@@

>>>>

For identifiability a sum-to-zero constraint is imposed on the components of the scaled iCAR/BYM model associated with each connected subgraph of the matrix $R$ \cite{Riebler2016}.
\item The BYM2 model, like other spatially-structure GMRF, relies on a neighbourhood matrix encoding the conditional dependencies between the data.

@@

\begin{equation*}
\begin{cases}
\mathrm{Parameters}
\begin{cases}
...next\\
\textbf{Models 3 to 6, spatial GMRF: GMRF with BYM2 structure for space}\\
\textbf{and exchangeable correlation structure between genotypes}\\
\mathrm{for}~f\in\{\alpha,\alpha'\},~(g_s,g_s')\in\{1,2\}^2,~\forall(z_s,z_s')\in \text{Set of postcodes}^2:\\
\mathrm{Latent~field}
\begin{cases}
f_{SPACE}(g_s) \sim 
BYM2\left(\sigma_{\text{SPACE}},\phi_{\text{SPACE}},R\right) \\
\mathrm{Corr}(f_{SPACE}(z_s, 1),f_{SPACE}(z_s, 2)) =\eta_{f_{\text{SPACE}}}
\end{cases}\\
\mathrm{Hyperparameters}
\begin{cases}
\eta_{f_{\text{SPACE}}}=  \frac{\exp(\eta_{f_{\text{SPACE}}}^*) - 1}{\exp(\eta_{f_{\text{SPACE}}}^*) + 2 - 1}\\
\eta_{f_{\text{SPACE}}}^* \sim \mathcal{N}\left(0,5\right)\\
\phi_{f_{SPACE}} \sim \mathcal{PC}_{\phi}\left(\lambda_{f_{SPACE}}\right)\\
\lambda_{f_{SPACE}} = \arg_{\in \mathbb{R}^+}: \Pr_{\lambda_{\sigma_{f_{\phi_{\text{SPACE}}}}}}\left(\phi_{f_{\text{SPACE}}}\leq\phi_{0}\right)=p_{\phi_{f_{\text{SPACE}}}}\\
\sigma_{f_{SPACE}} \sim \mathcal{PC}_{\sigma}\left(\lambda_{\sigma_{f_{SPACE}}}\right)\\
\lambda_{\sigma_{f_{SPACE}}} = -\frac{-\log\left(p_{\sigma_{f_{SPACE}}}\right)}{\sigma_{0}},~\Pr\left(\sigma >\sigma_{0}\right)=p_{\sigma_{f_{SPACE}}}\\
\left(\sigma_{0},p_{\sigma_{f_{SPACE}}}\right)=\left(10,0.01\right) \\
\left(\phi_{0},p_{\phi_{f_{SPACE}}}\right)=\left(0.5,0.5\right) \\
R :\begin{cases} 
\text{Delaunay Triangulation (model 3)}\\
\text{SOI subgraph of the Delaunay Triangulation (model 4)} \\
\text{1st-order Queen contiguity (model 5)} \\ 
\text{2nd-order Queen contiguity (model 6)} \\ 
\end{cases}
\end{cases}
\end{cases}
\end{cases}
\end{equation*}
\newpage

@@

```{r eval=FALSE, include=FALSE}
#NB: for grouping structure for BYM2 model:
https://mail.google.com/mail/u/0/#inbox/FMfcgzQZTMQQzvMCsRTqzlCgkTmSdSNz
```
